Knowledge \& the web: homework 2

### 2015-11-02 homework_2/hw2.tex
updated title and cleaned project

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\author{
  Katrien Laenen\\
  \and
  Gust Verbruggen\\
  \and
  Ward Schodts
}
\title{Knowledge \& the web: exercise session 4}
\begin{document}
\maketitle
\section{Interesting knowledge bases}
\begin{enumerate}

\item Musicbrainz
\item \url{data.nobelprize.org}
\item \url{http://datahub.io/dataset/zdb}
\item \url{ZDB}

\end{enumerate}
\section{Interesting questions}
\subsection{How many and wich European Parliants members were involved with criminal activities?}
\subsection{Which politicians have good chances of receiving a Nobel Price?}
\subsection{Which song came out on the birthday of a specific politician?}
\subsection{Which politician are murdered.}
\subsection{Which politician are stated in any document on ZDB.}
\subsection{Which politician have the most tv/radio appearences?}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\author{
  Katrien Laenen\\
  \and
  Gust Verbruggen\\
  \and
  Ward Schodts
}
\title{Knowledge \& the web: homework 2}
\begin{document}
\maketitle
\section*{Which politician have the most tv/radio appearences (on BBC)?}
